The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-29 manuscript/manuscript.qmd
Update dynamic noise vaccination values for manuscript

For each noise structure, we simulated five different magnitudes of noise ($\Lambda$).
$\Lambda$ was calculated as a multiple ($c$) of the average daily measles incidence ($\langle \Delta I_{M} \rangle$): $\Lambda = c \cdot \langle \Delta I_{M} \rangle \text{where} c \in	\{1, 2, 4, 6, 8 \}$.
For the Poisson-noise scenarios, independent draws from a Poisson distribution with mean $\lambda = \Lambda$ were simulated to produce the noise time series.
For the dynamical noise scenarios, the vaccination rate at birth was set to 85.4%, 73.8%, 50.8%, 27.9%, and 5.0% to produce equivalent mean daily noise values (to within 2 decimal places): $\Lambda = \langle \Delta I_{R} \rangle = c \cdot \langle \Delta I_{M} \rangle$.

>>>>

For each noise structure, we simulated five different magnitudes of noise ($\Lambda$).
$\Lambda$ was calculated as a multiple ($c$) of the average daily measles incidence ($\langle \Delta I_{M} \rangle$): $\Lambda = c \cdot \langle \Delta I_{M} \rangle \text{where} c \in	\{1, 2, 4, 6, 8 \}$.
For the Poisson-noise scenarios, independent draws from a Poisson distribution with mean $\lambda = \Lambda$ were simulated to produce the noise time series.
For the dynamical noise scenarios, the vaccination rate at birth was set to 85.38%, 73.83%, 50.88%, 27.89%, and 4.92% to produce equivalent mean daily noise values (to within 2 decimal places): $\Lambda = \langle \Delta I_{R} \rangle = c \cdot \langle \Delta I_{M} \rangle$.
